Supplement 2

### 2020-09-19 paper/supplement-2.Rmd
update search method.

Football related articles published in 2019 were studied. Three major
sports medicine databases were searched on May 20, 2020, using key terms and limits. 
The databases were: SPORTDiscus, Embase and Cinahl. A
list of the search terms and complete search statements are provided in
Table \@ref(tab:search-table-print) below.

@@

```{r notes-to-add-for-index, echo = FALSE, eval = FALSE}
# from sport discuss
# "Published Date: 20190101-20191231; English Abstract Available; Peer Reviewed"
# "Articles: 1,372"

# from Embase
# "#1 AND #2 AND [english]/lim AND 2019:py"
# "Articles: 1,756"

# from Cinahl
# "Published Date: 20190101-20191231; English Abstract Available; Peer Reviewed"
# "Articles: 735"
```

```{r search-table-print}
table_terms %>% 
  kable(caption = "Key search terms and complete search statements and limits for the databases, SPORTDiscuss, Embase, and Cinahl") %>% 
  kable_styling("striped",
                full_width = TRUE) 
```

@@

Articles were surveyed to determine: (a) whether a missing data
statement was included, or if missing data were acknowledged in a
figure/table; where data were missing, whether (b) data were considered
MCAR, MAR or MNAR; (c) imputation was used; (d) the method used for imputation; 
and (e) whether articles that did not include a missing data
statement shared their data. Two authors independently extracted the
data. Agreement was X%; discrepancies were resolved by NJT. Findings are
reported as the proportion and 95% confidence interval (CI). Confidence
intervals were calculated using the Clopper-Pearson method for the
binomial distribution [@Clopper1934],via the 'binom' package [@binom] in R (version 4.0.2) [@rcore].

>>>>

Football related articles published in 2019 were studied. Three major
sports medicine databases were searched on May 20, 2020, using key terms and limits. 
The databases were: SPORTDiscus, Embase and Cinahl. A
list of the search terms has been provided in
Table \@ref(tab:search-table-print) below.

@@

```{r search-table-print}
table_terms %>% 
  kable(caption = "Key search terms and complete search statements for the databases, SPORTDiscuss, Embase, and Cinahl") %>% 
  kable_styling("striped",
                full_width = TRUE) 
```

@@

Articles were surveyed to determine: (a) whether a missing data
statement was included, or if missing data were acknowledged in a
figure/table; where data were missing, whether (b) data were considered
MCAR, MAR or MNAR; (c) imputation was used; (d) the method used for imputation; 
and (e) whether articles that did not include a missing data
statement shared their data. Two authors independently extracted the
data. Agreement was X%; discrepancies were resolved by NJT. Findings are
reported as the proportion and 95% confidence interval (CI). Confidence
intervals were calculated using the Clopper-Pearson method for the
binomial distribution [@Clopper1934], via the 'binom' package [@binom] in R (version 4.0.2) [@rcore].
